Invasive lionfish present region-wide variation of allometric growth in the

### 2018-04-20 docs/Manuscript.Rmd
Added tag to Table 1
Deleted code that had been commented, no longer needed

Length-weight relationships (n = `r dim(review)[1]-1`) identified in literature were obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and Caribbean (n = 8). Information on sampling methods, sex differentiation, location, and depth ranges of each study was retrieved when available. Studies were assumed to include both genders if gender was unspecified. Locations where allometric studies were performed are shown in Figure \ref{fig:map} and \ref{tab:all_params}.

\clearpage

@@

ggplot() +
  geom_sf(data = W) +
  geom_point(data = review %>%
      mutate(N = ifelse(is.na(N), 1, N)),
    aes(x = lon, y = lat, fill = b, size = N), shape = 21) +
  theme_classic() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(20)) +
  theme(legend.background = element_blank(),
        panel.grid.major = element_line(colour = "transparent")) +
  # guides(colorbar = guide_legend(order = 0),
  #        size = guide_legend(order = 1,
  #                            direction = "horizontal",
  #                            title.position = "top")) +
  lims(x = c(-100, -60), y = c(9, 36)) +
  labs(x = "longitude", y = "latitude") +
  geom_text(aes(x = -70, y = 30), label = "North Atlantic\nOcean") +
  geom_text(aes(x = -90, y = 25), label = "Gulf of Mexico") +
  geom_text(aes(x = -75, y = 15), label = "Caribbean\nSea")

>>>>

Length-weight relationships (n = `r dim(review)[1]-1`) identified in literature were obtained for the North Atlantic (n = 1), Gulf of Mexico (n = 7,), and Caribbean (n = 8). Information on sampling methods, sex differentiation, location, and depth ranges of each study was retrieved when available. Studies were assumed to include both genders if gender was unspecified. Locations where allometric studies were performed are shown in Figure \ref{fig:map} and Table \ref{tab:all_params}.

<!-- \clearpage -->

@@

ggplot() +
  geom_sf(data = W) +
  geom_point(data = review %>%
      mutate(N = ifelse(is.na(N), 1, N)),
    aes(x = lon, y = lat, fill = b, size = N), shape = 21) +
  theme_classic() +
  scale_fill_gradientn(colors = colorRamps::matlab.like(20)) +
  theme(legend.background = element_blank(),
        panel.grid.major = element_line(colour = "transparent")) +
  lims(x = c(-100, -60), y = c(9, 36)) +
  labs(x = "longitude", y = "latitude") +
  geom_text(aes(x = -70, y = 30), label = "North Atlantic\nOcean") +
  geom_text(aes(x = -90, y = 25), label = "Gulf of Mexico") +
  geom_text(aes(x = -75, y = 15), label = "Caribbean\nSea")
